Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-25 paper-webserver.tex
EDIT: functionality section

% para covering ectyper & RGI
To further characterize strains ... serotyping, which detects the presence of specific cell surface antigens.
O-antigen and H-antigen typing, and VF determination use our ECTyper software.
ECTYper compares the user-submitted genomes against a curated set of sequences, an approach originally implemented in the VirulenceFinder \cite{joensen2014real} tool.
The Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive} maintains a set of known AMR genes and develops the RGI program .
Both ECTyper and RGI are based off of BLAST \cite{pmid2231712}.

>>>>

% para covering ectyper & RGI
To characterize strains, one approach is serotyping, which detects the presence of specific cell surface antigens.
ECTyper uses a curated set of O-type and H-type specific gene sequences and runs the Basic Local Alignment Search Tool (BLAST) \cite{pmid2231712} against the query genome, before ranking the determined serotype in order of probability.
A reference set of VFs sequences, obtained from literature review and available at \url{https://github.com/phac-nml/ecoli_vf}, is used with BLAST to determine associated VFs in a genome, an approach originally implemented in the VirulenceFinder program \cite{joensen2014real}
We difer to the RGI tool, based off of the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, maintains AMR gene determination.
